lfl: An \R{} Package for Linguistic Fuzzy Logic

### 2021-06-10 article.tex
Updates from Overleaf

First of all, we transform the \texttt{iris} data frame into fuzzy sets.
%
\input{chunks/chunk-casestudy-assoc-lcut}
%
This creates a data frame with each column representing linguistic expressions on original Iris data attributes.

We can search for association rules, convert the result into a \texttt{data.frame} and print first 6 rules as follows:
%
\input{chunks/chunk-casestudy-assoc-searchrules}
%

@@

>>>>

First of all, we transform the \texttt{iris} data frame into fuzzy sets:
%
\input{chunks/chunk-casestudy-assoc-lcut}
%
This creates a data frame with each column representing linguistic expressions on original Iris data attributes. We have opted for pentachotomical contexts, which cause each numeric variable to be transformed using 5 atomic linguistic expressions ``small'' (sm), ``lower medium'' (lm), ``medium'' (me), ``upper medium'' (um), and ``big'' (bi). The \texttt{hedges="-"} argument disables all linguistic hedges. The resulting \texttt{fsets} object contains 23 fuzzy sets: five for each of four original numeric variables (sepal/petal length/width) and three dichotomic fuzzy sets for species categories.

All association rules with species in consequent and the rest of variables in antecedent can be found by executing the following command:
%
\input{chunks/chunk-casestudy-assoc-searchrules}
%
The minimum support threshold of a rule was set to 0.05 while the minimum confidence is required to be at least 0.8. Such settings result in

@@

In \pkg{arules}, the process could be as follows:
%
\input{chunks/chunk-casestudy-assoc-arules}
%
